Empirical normative theories

### 2020-07-17 simple.tex
Clearer notations and a note about observable relations

\section{Next}
\NewDocumentCommand{\ileadstoe}{O{}}{⇝^{#1}_\exists}
\NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.

@@

\subsection{Falsifiability}
\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim. It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}

>>>>

\section{Next}
Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.

@@

\subsection{Falsifiability}
\commentOC{I should define $\Box(\hist \ileadsto \phi)$ iff it has been observed that $\hist \ileadsto \phi$. Then, axiom Correct observations (that is self-evident): $\Box(\hist \ileadsto \phi) ⇒ \hist \ileadsto \phi$ (what has been observed is). Supplementary axiom Falsification is enough (that is not self-evident): $\not\Box(\hist \ileadsto \phi) ⇒ \hist \nileadsto \phi$ (what has not been observed is not).}

\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim. It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}
